Exploring the Motives and Driving Forces Behind Modifications to APIs From a Software Evolution Perspective

### 2015-05-02 thesis/acm/paper.tex
Stuff

\category{D.2.7}{Software Engineering}{Distribution, Maintenance, Enhancement}[Restructuring, reverse engineering, and reengineering]
\category{K.6.3}{Computing Milieux}{Software Management}[Software Maintenance]

@@

\subsection{Research Questions} \label{rqs}
\begin{description}
\item[\textbf{RQ1:}] How do companies actively drive API evolution?
\item[\textbf{RQ1.1:}] To what extent can we reverse engineer API change decisions?
\item[\textbf{RQ2:}] How do APIs ``passively'' evolve?

@@

%Info from the interview, add to this section
Has been released, in the form we looked at (supports that we’re doing a ‘real’ case study)
They have “partners” which develop applications using their API. These applications are then used by the end-users of the camera.

@@

\section{Methodology} \label{methodology}
%Intro and summary
This study has been conducted using the case study methodology \cite{runeson2009guidelines}. The goal of the study was twofold. Firstly, the aim was to empirically \textit{explore} the motives behind changes to APIs and secondly, our ambition was to \textit{validate} the results' level of correctness by comparing our findings with the case company's explanation of their motives. Our research can be classified as an embedded case study \cite{yin2013case}, since both the API code and API documentation have been used as units of analysis.

@@

\section{RQ1} \label{results}

@@

%%Does this paragraph below belong here or somewhere else? Feels a bit odd!    W: Case Company Description I think
The API itself consisted of two major versions; 1.4 and 2.0. There were no intermediate versions between 1.4 and 2.0. Version 1.4 was actually the same version as 1.0, just with added build options for other hardware platforms. The changes therefore come from the changes between the two major versions. Given that there was an apparent "big bang" implementation of the new API, we have tried to determine what existed in the previous version, what was re-implemented and what is brand new.

@@

%%Relate it to Categories
The information gathered from the interview suggests (!!!Better word than this?) that were correct in our choice of enhancive for this change. Once more there was no inclusion of an appropriate subcategory.

@@

In regards to re-implementations, during the interview it was mentioned that one intent behind the re-implementations was to bring them in-line with the newly created functionality which take advantage of Glib, a new kind of error handling and extensive use of callbacks.

@@

\section{RQ2 Lehman}
This section will present results related to \textbf{RQ2}. The information introduced was collected during the interview with the case company.

@@

\section{Discussion}

@@

\subsection{RQ2}
The general conclusion: 
5 laws clearly apply
2 laws probably apply (not significant)
1 law clearly doesn't apply

>>>>

\category{D.2.7}{Software Engineering}{Distribution, Maintenance, Enhancement}[Restructuring, reverse engineering, and re-engineering]
\category{K.6.3}{Computing Milieux}{Software Management}[Software Maintenance]

@@

\subsection{Research Questions} \label{rqs}
\begin{description}
\item[\textbf{RQ1}] How do companies actively drive API evolution?
\item[\textbf{RQ1.1}] To what extent can we reverse engineer API change decisions?
\item[\textbf{RQ2}] How do APIs ``passively'' evolve?

@@

%Info from the interview, add to this section
Has been released, in the form we looked at (supports that we’re doing a ``real'' case study)
They have partners which develop applications using their API. These applications are then used by the end-users of the camera.

@@

\section{Methodology} \label{methodology}
%Intro and summary
This study has been conducted using the case study meth-odology \cite{runeson2009guidelines}. The goal of the study was twofold. Firstly, the aim was to empirically \textit{explore} the motives behind changes to APIs and secondly, our ambition was to \textit{validate} the results' level of correctness by comparing our findings with the case company's explanation of their motives. Our research can be classified as an embedded case study \cite{yin2013case}, since both the API code and API documentation have been used as units of analysis.

@@

\section{Results RQ1} \label{results}

@@

%%Does this paragraph below belong here or somewhere else? Feels a bit odd!    W: Case Company Description I think
The API itself consisted of two major versions; 1.4 and 2.0. There were no intermediate versions between 1.4 and 2.0. Version 1.4 was actually the same version as 1.0, just with added build options for other hardware platforms. The changes therefore come from the changes between the two major versions. Given that there was an apparent ``big bang'' implementation of the new API, we have tried to determine what existed in the previous version, what was re-implemented and what is brand new.

@@

%%Relate it to Categories
The information gathered from the interview supported that were correct in our choice of enhancive for this change. Once more there was no inclusion of an appropriate subcategory.

@@

During the interview it was mentioned that one intent behind the re-implementations was to bring them in line with the newly created functionality which takes advantage of Glib, a new kind of error handling and extensive use of callbacks.

@@

\section{RQ2 Lehman}
This section will present results related to \textbf{RQ2}. The results are structured around how much our results indicate that each of Lehman's laws apply to platform APIs.

@@

\section{Discussion}
In this section we will discuss the results of our study.

@@

\subsection{RQ2}
The 
The general conclusion: 
5 laws clearly apply
2 laws probably apply (not significant)
1 law clearly doesn't apply
